Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
edits after full read through

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010} 
  When cross-linked, these materials can function as mechanically
  strong separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase has hexagonally packed, straight pores which is the ideal geometry 
  for high throughtput separations. However, the synthesis of H\textsubscript{II}
  membranes with highly aligned hexagonal mesophases has been a challenge that
  has been met with limited success and has prevented the material's viability 
  as a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The Q\textsubscript{I} 
  consists of a three dimensional network of tortuous and interconnected pores. 
  It's more facile synthesis has yielded it more success. The latest 
  Q\textsubscript{I} phase membranes have been shown to exhibit selectivities
  higher than commercial NF and RO membranes permeabilities higher than commercial
  RO membranes.~\cite{dischinger_application_2017}

@@

  Molecular dynamics (MD) simulations can give us mechanistic insights with
  atomistic resolution so that we can provide detailed descriptions of small
  solute transport within LLC membrane nanopores and intelligently design new
  membranes for solute-specific separations. In our previous work, we used MD
  simulations to determine the most likely structure of the hexagonal phase
  formed by the monomer Na-GA3C11, expanding upon the most recent experimental
  characterization.~\cite{coscia_understanding_2018,feng_thin_2016} We developed
  techniques to simulate the hexagonal phase formed by neat monomer as well as
  with varying amounts of water in the pores.

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character within the pores of an H\textsubscript{II} phase LLC. The pores of the 
  H\textsubscript{II} phase have a similar topology to the Q\textsubscript{I} phase but
  is a simpler geometry to model. In future studies, we will extend our techniques to
  the Q\textsubscript{I} phase.

@@

  We first address the structure of the membrane nanopores. Previously, we
  studied dry membrane systems and some systems with low water content. We showed
  that those systems have rather crowded pores with high concentrations of monomer
  head groups, sodium ions and water, where applicable. Here we build systems with
  appreciable amounts of water, 5 and 10\% by weight, and analyze how the radial
  density of monomer components and water change compared to our previous results.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis (as described below and in the supporting information) are available 
  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
  appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

@@

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF as it has been used extensively for use with organic molecules.
  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from OpenEye Scientific Software.

@@

  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
  using a broad range of water concentrations. In the literature, the system 
  studied in this work is typically synthesized with close to 10 wt\% water.
  \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
  system is likely fully hydrated with less than 7 wt\% water.~\cite{resel_h2-phase_2000}
  Excess water fills space between hexagonal mesophases. We decided to test 
  systems with two different water contents: 5 and 10 wt\%.

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region. We 
  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
  %BJC3: added reference to later section. 
  %MRS3: We probably need to mention the amount of water there is; 40% is in the tail.  We should probably discuss density; that because of the larger tail volume, the density is about 1/X in the distal region than in the pore.

@@

  To study a given solute, we added 6 solute molecules, equally spaced in $z$, to the
  center of each pore of the equilibrated cross-linked configuration, for a total of 24
  solute molecules. We chose 6 solutes per pore to provide a balance of a useful amount of 
  data for generating statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
  with pressure controlled by the Parrinello-Rahman barostat.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate 
  trends in $D$, we will calculate trends in trends in solute MSDs. For Brownian
  particles, $D$ is proportional to the MSD divided by time, $t$. Therefore, 
  we analyze qualitative trends in solute MSDs according to:
  \begin{equation}
  MSD = \dfrac{k_bTt}{6\pi\eta fr}
  \label{eqn:msd-stokes-einstein}
  \end{equation}
  We hold $t$ constant in our simulations in order to make side-by-side comparisons.

@@

  %BJC: another option is to fit to water which IS Brownian in the 10 wt% system.
  In order to make qualitative comparisons, we fit Equation~\ref{eqn:msd-stokes-einstein}
  so that it passed through the highest solute MSD. We assumed that the solute
  with the highest MSD exhibited the closest to Brownian behavior and therefore could set
  a rough boundary between subdiffusive, Brownian and superdiffusive MSDs. As a lower
  bound to our appoximation, we also plotted the uncorrected version of 
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the same 
  value as the corrected curve for large radii. 
  % BJC: Set really high intersection value. Converges quickly (i.e. critical radius
  % (the radius where curves intersect) of 2.5 nm looks almost the same as critical
  % radius of 100 nm. I don't think this necessarily needs to be proved anywhere

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range of distances and angles.

@@

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibrations that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density (see 
  Figure~\ref{fig:total_density})as well as oxygen atoms at the ends of each
  monomer tail which can further stabilize water molecules.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
  of both membranes are in the pore center and in the tail region, furthest from the pore
  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
  \end{figure}

@@

  Sodium coordinates with both water and carboxylate moieties from the head
  groups in the pores. Sodium coordinates with 3.4 water molecules in bulk 
  solution (see Section~\ref{method:coordination}), but on average in the pores,
  coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
  molecules in the 5 wt\% system. The sodium ions additionally coordinate with
  1 carboxylate group in the 10 wt\% water system and 0.8 carboxylate groups 
  in the 5 wt\% water system. This behavior likely slows the motion of the 
  sodium ions considerably compared to bulk water.
  %MRS2: is one sodium per carboxylate group correct?
  %BJC3: yes, if sodium within cutoff of both oxygens, it is only counted once.
  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
  % since the averages were divided by 800 instead of 400

@@

  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this paper to 
  solutes in or near the pore center. Transport of solutes in the pores 
  %MRS3:
  %will 
  is likely to be
  be the 
  limiting factor that determines permeability and rejection. Although tail transport of water in the 
  the 5 wt\% water system is faster than pore transport, water transport overall is significantly slower
  than in the 10 wt\% system. For practical applications, a membrane with water 
  transport properties comparable to the 10 wt\% system is far more feasible than
  the 5 wt\% system.

@@

  As with water and sodium, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
  water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it.

  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

@@

  The complex and non-homogeneous structure of the membrane leads to radially
  dependent transport mechanisms. In general, we observed that hops 
  made in the pore region are about 59\% larger than those made outside
  the pore region (see Figure~\ref{fig:hop_lengths}). There is a high 
  resistance to movement in the alkane-dense head group and tail regions
  while, in the pore region, solutes can move relatively freely since it 
  is primarily composed of water molecules. However, time spent in the 
  pore region does not necessarily lead to more frequent hopping. The 
  largest solutes in this study spend the most time in the pore region
  (see Figure~\ref{fig:frac_time}), but many hop with a below-average
  frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
  controlled by membrane properties other than alkane density must be prevalent.

@@

  %In addition to solute trapping in dense monomer regions, 
  We observe a second trapping mechanism caused by preferential hydrogen 
  bonding between hydrogen bond donor solutes and monomer head groups. To 
  continue with our ethanol example, we observe that 64\% of ethanol 
  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
  and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
  head groups, 25\% go to the ether linkages connecting the monomers tails to the 
  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molecules in pores 
  carboxylate oxygen atoms in the pore than there are water molecules yet more
  hydrogen bonds are donated to them. The stability of hydrogen bonds with 
  carboxylate oxygen atoms is high because they have a negative charge
  with no neutralizing positive charges nearby. Additionally, on average, 
  each sodium ion is coordinated to 1.7 water molecules meaning an appreciable
  fraction of the water molecules occupying the pore region are usually 
  coordinated to a sodium ion which decreases their availability to accept 
  hydrogen bonds from solutes.
  % MRS1: this should lead to reduced ability to solvate positive things, but 
  % shouldn't reduce H-bonding that much?
  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.

@@

  Finally, we observe slowing or immobilization of solutes that associate with
  sodium counterions. Much like water, the polarity of the solutes creates 
  regions of high electron density, modeled using partial negative charges, 
  which are stabilized through electrostatic interactions with sodium ions. 
  In Figure~\ref{fig:na_coordination}, we've plotted the average percentage
  of solutes coordinated to a sodium ion each frame as well as the
  95\textsuperscript{th} percentile of sodium association lifetimes. The degree and length of 
  coordination between solutes and sodium in the 5 wt\% water system is higher
  in all cases than that in the 10 wt\% water systems. The crowded pores of 
  the 5 wt\% water system forces sodium ions in close proximity to solutes.

>>>>

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
  When cross-linked, these materials can function as mechanically strong
  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
  has hexagonally packed, straight pores which is the ideal geometry for high
  throughtput separations. However, the synthesis of H\textsubscript{II}
  membranes with highly aligned hexagonal mesophases has been a challenge that
  has been met with limited success and has prevented the material's viability as
  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
  and interconnected pores.  It's more facile synthesis has yielded it more
  success. The latest Q\textsubscript{I} phase membranes have been shown to
  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
  higher than commercial RO membranes.~\cite{dischinger_application_2017}

@@

  % TODO: monomer structure
  Molecular dynamics (MD) simulations can give us mechanistic insights with
  atomistic resolution so that we can provide detailed descriptions of small
  solute transport within LLC membrane nanopores and intelligently design new
  membranes for solute-specific separations. In our previous work, we used MD
  simulations to determine the most likely structure of the hexagonal phase
  formed by the monomer Na-GA3C11, expanding upon the most recent experimental
  characterization.~\cite{coscia_understanding_2018,feng_thin_2016} We developed
  techniques to simulate the hexagonal phase formed by neat monomer as well as
  with varying amounts of water in the pores.

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20
  uncharged polar solutes with varying size, chemical functionality and
  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
  the Q\textsubscript{I} phase but their geomeitry is simpler to model. In future
  studies, we will extend our techniques to the Q\textsubscript{I} phase.

@@

  We begin our analysis by studying the structure of the membrane nanopores.
  Previously, we studied dry membrane systems and some systems with low water
  content. We showed that those systems have rather crowded pores with high
  concentrations of monomer head groups, sodium ions and water, where applicable.
  Here we build systems with appreciable amounts of water, 5 and 10\% by weight,
  and analyze how the radial density of monomer components and water change
  compared to our previous results.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis (as described below and in the Supporting Information) are available 
  online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}. The 
  appropriate scripts to use for the subsequent calculations are summarized in 
  Table~\ref{S-table:python_scripts} of the Supporting Information. We ran all 
  MD simulations and energy minimizations using GROMACS 2018.3.~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

@@

  We parameterized the interaction potential for the monomer and solutes using
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with
  AmberTools16~\cite{case_ambertools16_2016}.  We use GAFF as it has been used
  extensively with organic molecules.  We assigned atomic charges using the
  am1bccsym method of \texttt{molcharge} included with QUACPAC from OpenEye
  Scientific Software.

@@

  Stable H\textsubscript{II} phases, assembled with monomer Na-GA3C11, can be formed
  using a broad range of water concentrations. In the literature, the system 
  studied in this work is typically synthesized with close to 10 wt\% water.
  \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
  system is likely fully hydrated with less than 7 wt\% water.~\cite{resel_h2-phase_2000}
  Excess water fills space between hexagonal mesophases. We decided to test 
  systems with two different water contents: 5 and 10 wt\%.

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution function of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region. We 
  justify this decision with better context in Section~\ref{section:transport_water_sodium}.
  %MRS2: seems like here is where we need to provide the justification for this decision, since the decision is described here (or, explain how we will justify it later)
  %BJC3: added reference to later section. 
  %MRS3: We probably need to mention the amount of water there is; 40% is in the tail.  We should probably discuss density; that because of the larger tail volume, the density is about 1/X in the distal region than in the pore.

@@

  To study a given solute, we added 6 solute molecules, equally spaced in $z$, to the
  center of each pore of the equilibrated cross-linked configuration, for a total of 24
  solute molecules. We chose 6 solutes per pore to provide a balance of a useful amount of 
  data for generating statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate at 300K for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
  with pressure controlled by the Parrinello-Rahman barostat.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate 
  trends in $D$, we will calculate trends in solute MSDs. For Brownian
  particles, $D$ is proportional to the MSD divided by time, $t$. Therefore, 
  we analyze qualitative trends in solute MSDs according to:
  \begin{equation}
  MSD = \dfrac{k_bTt}{6\pi\eta fr}
  \label{eqn:msd-stokes-einstein}
  \end{equation}
  We hold $t$ constant in our simulations in order to make side-by-side comparisons.

@@

  %BJC: another option is to fit to water which IS Brownian in the 10 wt% system.
  We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
  highest solute MSD. We assumed that the solute with the highest MSD exhibited
  the closest to Brownian behavior and therefore could set a rough boundary
  between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
  appoximation, we also plotted the uncorrected version of
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
  same value as the corrected curve for large radii. 
  % BJC: Set really high intersection value. Converges quickly (i.e. critical radius
  % (the radius where curves intersect) of 2.5 nm looks almost the same as critical
  % radius of 100 nm. I don't think this necessarily needs to be proved anywhere

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  %TODO: reference for VMD
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range of distances and angles.

@@

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibrations that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density (see 
  Figure~\ref{fig:total_density}) as well as oxygen atoms at the ends of each
  monomer tail which can further stabilize water molecules.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
  of both membranes are in the pore center and in the distal tail region, furthest from the pore
  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
  \end{figure}

@@

  Sodium coordinates with both water and carboxylate moieties from the head
  groups in the pores. Sodium coordinates with 3.4 water molecules in bulk 
  solution (see Section~\ref{method:coordination}), but on average in the pores,
  coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
  molecules in the 5 wt\% system. The sodium ions additionally coordinate with
  1 carboxylate group in the 10 wt\% water system and 0.8 carboxylate groups 
  in the 5 wt\% water system. This behavior likely slows the motion of the 
  sodium ions considerably compared to in bulk water.
  %MRS2: is one sodium per carboxylate group correct?
  %BJC3: yes, if sodium within cutoff of both oxygens, it is only counted once.
  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
  % since the averages were divided by 800 instead of 400

@@

  Because the MSD of water in the pores of the 10 wt\% system is significantly
  higher than that in the tails, we restrict our studies of transport in this
  paper to solutes in or near the pore center. Transport of solutes in the pores
  is likely to be the limiting factor that determines permeability and rejection.
  Although tail transport of water in the the 5 wt\% water system is faster than
  pore transport, water transport overall is significantly slower than in the 10
  wt\% system. For practical applications, a membrane with water transport
  properties comparable to the 10 wt\% system is far more feasible than the 5
  wt\% system.

@@

  As with water and sodium, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (see Figures~\ref{fig:all_msds_5wt} and~\ref{fig:all_msds_10wt}). The fastest moving solute in both cases, 
  methanol, has an MSD about 26 times larger in the 10 versus the 5 wt\%
  water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
  %TODO: add indication of scale
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

@@

  The complex and inhomogeneous structure of the membrane leads to radially
  dependent transport mechanisms. In general, we observed that hops 
  made in the pore region are about 59\% larger than those made outside
  the pore region (see Figure~\ref{fig:hop_lengths}). There is a high 
  resistance to movement in the alkane-dense head group and tail regions
  while, in the pore region, solutes can move relatively freely since it 
  is primarily composed of water molecules. However, time spent in the 
  pore region does not necessarily lead to more frequent hopping. The 
  largest solutes in this study spend the most time in the pore region
  (see Figure~\ref{fig:frac_time}), but many hop with a below-average
  frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
  controlled by membrane properties other than alkane density must be prevalent.

@@

  %In addition to solute trapping in dense monomer regions, 
  We observe a second trapping mechanism caused by preferential hydrogen 
  bonding between hydrogen bond donor solutes and monomer head groups. To 
  continue with our ethanol example, we observe that 64\% of ethanol
  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
  and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
  head groups, 25\% go to the ether linkages connecting the monomer tails to the 
  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molecules in pores 
  carboxylate oxygen atoms in the pore than there are water molecules yet more
  hydrogen bonds are donated to them. The stability of hydrogen bonds with 
  carboxylate oxygen atoms is high because they have a negative charge
  with no neutralizing positive charges nearby. Additionally, on average, 
  each sodium ion is coordinated to 1.7 water molecules meaning an appreciable
  fraction of the water molecules occupying the pore region are usually 
  coordinated to a sodium ion which decreases their availability to accept 
  hydrogen bonds from solutes.
  % MRS1: this should lead to reduced ability to solvate positive things, but 
  % shouldn't reduce H-bonding that much?
  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.

@@

  Finally, we observe slowing or immobilization of solutes that associate with
  sodium counterions. Much like water, the polarity of the solutes creates 
  regions of high electron density, modeled using partial negative charges, 
  which are stabilized through electrostatic interactions with sodium ions. 
  In Figure~\ref{fig:na_coordination}, we've plotted the average percentage
  of solutes coordinated to a sodium ion each frame as well as the
  95\textsuperscript{th} percentile of sodium association lifetimes. The degree and length of 
  coordination between solutes and sodium in the 5 wt\% water system is higher
  in all cases than that in the 10 wt\% water systems. The crowded pores of 
  the 5 wt\% water system force sodium ions in close proximity to solutes.
